Trends of SDR in Thessaloniki

### 2023-07-10 Article.Rmd
Commit 2023-07-10 20:13

As global radiation clear sky reference we are using the Haurwitz’s model, adjusted for our site with a factor of `r signif(alpha,3)` (Eq.\ \ref{eq:ahau}).
The selection of a clear sky reference model, was based on SDR observation from the period 2016 – 2021.
Where, after an iterative optimization of eight simple models (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with different factors.
We found, that Haurwitz’s model, adjusted with a factor of `r signif(alpha,3)` has the lower root mean squared error (RMSE). 
The tried models are described by @Reno2012 and tested by @Reno2016.
The iterative optimization method, for the selection of the reference is discussed by @Long2000 and @Reno2016.

@@

>>>>

As SDR clear sky reference we are using the radiation model by Haurwitz’s, adjusted for our site with the factor  $a = `r signif(alpha,3)`$ (Eq.\ \ref{eq:ahau}), resulted by an iterative optimization process.
The selection of a clear sky reference model, was based on SDR observation from the period 2016 – 2021.
Where, after an iterative optimization of eight simple models (Daneshyar–Paltridge–Proctor, Kasten–Czeplak, Haurwitz, Berger–Duffie, Adnot–Bourges–Campana–Gicquel, Robledo-Soler, Kasten and Ineichen-Perez) with a wide range factors.
We found, that Haurwitz’s model, adjusted with a factor of `r signif(alpha,3)` has one of the lowest root mean squared error (RMSE), while retains most of our data. 
The tried models are described in more details by @Reno2012 and tested by @Reno2016.
The iterative optimization method, for the selection of the reference is described by @Long2000 and @Reno2016.
The target of the optimization was the minimizing of the function .......

\begin{equation}
f(a)=\frac{1}{n}\sum_{i=1}^{n}( \text{SDR}_{\text{meas},CS,i} - a \times \text{SDR}_{\text{ref},CS,i})^2
\end{equation}

@@

${MSE}={Cost}=\frac{1}{n}\sum_{i=1}^{n}(A_i - B_i)^2$
